\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
Add files via upload
just spelling / removed those two notes you had

% DAN 
The three graphs depict packets per 10 seconds for a the compete pcap sample, followed by traffic generated on the 20th and 22nd. The traffic was divided in this way to logically separate the behavior associated with each time sequence. The story of the infected host is encapsulated on the first day, whereas the second day exhibits indirect behavior of the infected host as the machine has been taken offline.

@@

Cryptostorm VPN connect over TLS 
192.36.27.5 -> Amsterdam IP for onion (Entry node)
103.198.0.2     45jngpxc4cgsxqxc.onion.link -> Singapore

@@

% DAN
On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence from what appears to be a spam mail. A mail with an attachment, potentially a Microsoft Word document, is fetched after a "503 Backend fetch failed" response. The following request is made to a destination IP associated with an onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those circumventing censorship but also those who exploit it for profit. The ".link" allows for for convenience at the expense of privacy, as your service provider can see your what content you are requesting \cite{onionlink}. The host also visited  torstorm.org domain, which offers a similar service. This allowed the target system to visit a TOR hidden services hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of a malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}. Please refer to appendix A for the TCP conversation of the payload delivery.

@@

Next we see a query for the domain cryptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. Cryptostorm uses openVPN to establish a secure VPN connection. The target host uses TLS to tunnel the openVPN connection to avoid blocking of the protocol. This is a feature provided by Cryptostorm which encrypts the TCP handshake to obscure the openVPN traffic \cite{tls}.

@@

The openVPN connection provides a secure communication channel for remote interaction with the host. This traffic is encrypted but DNS queries leak from the compromised host giving away precious information about the malware's behavior. We assume that this is an oversight made by the malware developers, as DNS resolution should happen over an encrypted channel.  DNS is a protocol that provides valuable insights to ISPs and intelligence agencies conducting surveillance. DNSsec provides tries to find a solution to this problem, by encrypting DNS \cite{dnssec}.

The DNS leaks provide insights into the TOR hidden services that are being accessed via the Cryptostorm VPN. The domains queried are all associated with TOR hidden service payment portals used by attackers to receive Cryptocurrency payments \cite{hybrid}. Once again we see the use of services that allow insecure access to TOR by regular web browses.

@@

The target host ceases to exist on the networking failing to respond to even ARP broadcasts from this point forward.

%Tor2web listing

Windows NT 6.1

Malicious IPs 
103.198.0.2:80
192.36.27.5:443
192.36.27.5:80
192.64.119.254:80

%\lstinputlisting[language=html]{evilstats.txt}

@@

The default gateway 10.0.0.2 broadcasted asking for compromised host. The broadcast was made 485 times. This could possibly indicate the command and control server attempting to reestablish communication with the target, as the default gateway attempted to ARB probe for the host. This assumes that the network has no firewall in place, or one that is misconfigured. Since packets entering the network should be blocked unless they are solicited from inside the network, as part of an on going connection. Thus the best explanation for the anomalous ARP probes are that the C2 server is checking whether his compromised hosts are still online.

>>>>

% DAN 
The three graphs depict packets per 10 seconds for the compete pcap sample, followed by traffic generated on the 20th and 22nd. The traffic was divided in this way to logically separate the behavior associated with each time sequence. The story of the infected host is encapsulated on the first day, whereas the second day exhibits indirect behavior of the infected host as the machine has been taken offline.

@@

@@

% DAN
On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence from what appears to be a spam mail. A mail with an attachment, potentially a Microsoft Word document, is fetched after a "503 Backend fetch failed" response. The following request is made to a destination IP associated with an onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those circumventing censorship but also those who exploit it for profit. The ".link" allows for for convenience at the expense of privacy, as your service provider can see what content you are requesting \cite{onionlink}. The host also visited  torstorm.org domain, which offers a similar service. This allowed the target system to visit a TOR hidden service hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of a malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}. Please refer to appendix A for the TCP conversation of the payload delivery.

@@

Next we see a query for the domain cyrptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. Cryptostorm uses openVPN to establish a secure VPN connection. The target host uses TLS to tunnel the openVPN connection to avoid blocking of the protocol. This is a feature provided by Cryptostorm which encrypts the TCP handshake to obscure the openVPN traffic \cite{tls}.

@@

The openVPN connection provides a secure communication channel for remote interaction with the host. This traffic is encrypted but DNS queries leak from the compromised host giving away precious information about the malware's behavior. We assume that this is an oversight made by the malware developers, as DNS resolution should happen over an encrypted channel.  DNS is a protocol that provides valuable insights to ISPs and intelligence agencies conducting surveillance. DNSsec tries to find a solution to this problem by encrypting DNS \cite{dnssec}.

The DNS leaks provide insights into the TOR hidden services that are being accessed via the Cryptostorm VPN. The domains queried are all associated with TOR hidden service payment portals used by attackers to receive Cryptocurrency payments \cite{hybrid}. Once again we see the use of services that allow insecure access to TOR by regular web browsers.

@@

The target host ceases to exist on the network failing to respond to even ARP broadcasts from this point forward.

@@

The default gateway 10.0.0.2 broadcasted asking for the compromised host. The broadcast was made 485 times. This could possibly indicate the command and control server attempting to reestablish communication with the target, as the default gateway attempted to ARB probe for the host. This assumes that the network has no firewall in place, or one that is misconfigured. Since packets entering the network should be blocked unless they are solicited from inside the network, as part of an on going connection. Thus the best explanation for the anomalous ARP probes are that the C2 server is checking whether his compromised hosts are still online.
